The Galactic Delay-Time Distribution of Type Ia Supernovae:\\ A Chemical Evolution Perspective

### 2023-07-21 src/tex/ms.tex
[showyourwork] overleaf sync

We explore four different functional forms for the SN Ia DTD: a power-law, a broken power-law with an initial flat plateau, an exponential, and an exponential with a prompt Gaussian component, with a few different parameterizations for each. Figure \ref{fig:dtds} presents these DTDs as a function of time since star formation.

@@

\paragraph{Prompt} A DTD in which 50\% of SNe Ia belong to a ``prompt'' Gaussian component at small $t$ and the other 50\% form an exponential tail at large $t$, normalized by $D_{t_p,\sigma,\tau}$:
\begin{equation}
    R(t) = D_{t_p,\sigma,\tau} \Big[e^{-\frac{(t-t_p)^2}{2\sigma^2}} + e^{-t/\tau}\Big]
    \label{eq:prompt-dtd}
\end{equation}
Following the two-population model from \citet{Mannucci2006-TwoPopulations}, we take $t_p=50$ Myr, $\sigma=15$ Myr, and $\tau=3$ Gyr, which results in roughly 50\% of SNe Ia exploding within $t<100$ Myr.

@@

\begin{deluxetable*}{lll}
\tablecaption{Summary of SN Ia DTD models explored in this paper.\label{tab:dtds}}
\tablehead{
\colhead{Model} & \colhead{Parameters} & \colhead{Similar to}
}
\startdata
Power-law   & $\alpha=-1.1$                 & \citet[][field]{Maoz2017-CosmicDTD}; 
                                              \citet{Wiseman2021-DESRates}              \\
Power-law   & $\alpha=-1.4$                 & \citet[][cluster]{Maoz2017-CosmicDTD}; 
                                              \citet{Heringer2019-FieldGalaxyDTD}       \\
Plateau     & $W=0.3$ Gyr, $\alpha=-1.1$    & \citet[][CLOSE DD]{Greggio2005-AnalyticalRates} \\
Plateau     & $W=1.0$ Gyr, $\alpha=-1.1$    & \citet[][WIDE DD]{Greggio2005-AnalyticalRates} \\
Triple-system   & $f_{\rm init}=0.05f_{\rm peak}$, $t_{\rm rise}=0.5$ Gyr, & \citet{Rajamuthukumar2022-TripleEvolution} \\
            & $W=0.5$ Gyr, $\alpha=-1.1$ & \\
Exponential & $\tau=1.5$ Gyr    & \citet[][SD]{Greggio2005-AnalyticalRates};
                                  \citet{Schonrich2009-RadialMixing};       \\
            &                   & \citet{Weinberg2017-ChemicalEquilibrium}  \\
Exponential & $\tau=3.0$ Gyr    & --- \\
Prompt      & $t_{\rm max}=0.05$ Gyr, $\sigma=0.015$ Gyr, & \citet{Mannucci2006-TwoPopulations} \\
            & $\tau=3.0$ Gyr & \\
\enddata
\end{deluxetable*}

@@

\begin{figure*}
    \centering
    \includegraphics{figures/star_formation_histories.pdf}
    \caption{The surface densities of star formation $\dot \Sigma_*$ (first row), gas infall $\dot \Sigma_{\rm in}$ (second row), and gas mass $\Sigma_{\rm gas}$ (third row), and the star formation efficiency timescale $\tau_*$ (fourth row) as functions of simulation time for our four model SFHs: inside-out (first column; see Equation \ref{eq:insideout-sfh}), late-burst (second column; see Equation \ref{eq:lateburst-sfh}), early-burst (third column; see Equations \ref{eq:earlyburst-ifr} and \ref{eq:earlyburst-taustar}), and two-infall (fourth column; see Equation \ref{eq:twoinfall-ifr}). In each panel, we plot curves for the zones which have inner radii of 4 kpc (yellow), 6 kpc (orange), 8 kpc (red), 10 kpc (violet), 12 kpc (indigo), and 14 kpc (blue).}
    \label{fig:sfhs}
    \script{star_formation_histories.py}
\end{figure*}

@@

All models are run for a duration of $t_{\rm max}=13.2$ Gyr with a time-step of $\Delta t=0.01$ Gyr. We adopt an outflow mass-loading factor $\eta\equiv \dot M_{\rm out}/\dot M_*=2.15$ \citep[see Equation 8 from][]{Johnson2021-Migration} and a star formation efficiency timescale $\tau_*\equiv M_{\rm gas}/\dot M_*=2$ Gyr. We adopt a continuous recycling prescription \citep[see Equation 2 from][]{JohnsonWeinberg2020-Starbursts}. Unless otherwise specified, we adopt the inside-out star formation rate (Equation \ref{eq:insideout-sfh}) evaluated at $R_{\rm gal}=8$ kpc, with timescales $\tau_{\rm rise}=2$ Gyr and $\tau_{\rm sfh}=15.1$ Gyr, and our models have an initial gas mass $M_{\rm gas,0}=0$. Unless otherwise specified, we assume a minimum SN Ia delay time of 40 Myr. A summary of these one-zone fiducial parameters is presented in Table \ref{tab:onezone-parameters}.

@@

\subsection{The SN Ia Delay-Time Distribution}

Adjusting the parameters of the DTD affects how steeply the abundance track in [Fe/H]-[O/Fe] space falls from its initial ``plateau'' and the location of the ``knee.'' Figure \ref{fig:onezone-slope-timescale} shows abundance tracks from one-zone models which assume different slopes of a power-law DTD or different timescales of an exponential DTD. A steeper power-law slope results in a steeper decline in [O/Fe] and a lower knee, as does a shorter exponential timescale. The consequence is that a very shallow power-law produces a similar abundance track to a very steep exponential, which suggests these models may be difficult to distinguish in this parameter space. However, these cases can be distinguished by their MDFs and [O/Fe] distributions, where the power-law DTD produces a narrower, less skewed distribution while the exponential DTD produces a broader, more skewed distribution. In the [O/Fe] distribution especially, an exponential DTD with a 6 Gyr timescale produces a large number of high-$\alpha$ stars.

\begin{figure}
    \centering
    \includegraphics{figures/onezone_powerlaw_slope.pdf}
    \caption{\textit{Center:} Abundance tracks in the [Fe/H]-[O/Fe] plane for one-zone models with a power-law DTD. The dotted, dashed, and solid curves represent models with power-law slopes $\alpha=-0.8$, $-1.1$, and $-1.4$, respectively. In all cases a minimum SN Ia delay time of 40 Myr is assumed. \textit{Top:} Metalliticy distribution functions (MDFs) generated by the one-zone models. \textit{Right:} Distributions of [O/Fe] generated by the one-zone models.}
    \label{fig:onezone-powerlaw-slope}
    \script{onezone_powerlaw_slope.py}
\end{figure}

@@

@@

A 150 Myr minimum delay time is incompatible with the prompt DTD model, which has $\sim 50$\% of SNe Ia explode in the first 100 Myr, and would have a negligible effect on the triple-system DTD as its relative SN Ia rate is so low at early times.

@@

\begin{figure}
    \centering
    \includegraphics{figures/onezone_sfh.pdf}
    \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with varying star formation history (SFH). An exponential DTD with $\tau=1.5$ Gyr is assumed in all models.}
    \label{fig:onezone-sfh}
    \script{onezone_sfh.py}
\end{figure}

@@

% \begin{figure}
%     \centering
%     \includegraphics{figures/greggio05_dtd.pdf}
%     \caption{Analytical DTDs computed by \citet{Greggio2005-AnalyticalRates}. The solid red curve represents the SD DTD for Chandrasekhar explosions, while the green and blue solid curves represent, respectively, the CLOSE and WIDE formulations of a DD DTD. The best-fit approximations for the DD DTDs (see Equation \ref{eq:greggio05-approx}) are represented by the dashed olive and cyan curves, respectively. All DTDs are normalized to unity.}
%     \label{fig:greggio05-dtd}
%     \script{greggio05_dtd.py}
% \end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{figures/onezone_twopopulation.pdf}
    \caption{One-zone model abundance tracks and distributions for variants of the prompt DTD.}
    \label{fig:onezone-prompt}
    \script{onezone_twopopulation.py}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics{figures/feh_df_sfh.pdf}
    \caption{Distributions of [Fe/H] for multi-zone simulations with different SFHs. Each row presents distributions of stars within a range of absolute midplane distance: $1\leq|z|<2$ kpc (\textit{top}), $0.5\leq|z|<1$ kpc (\textit{middle}), and $0\leq|z|<0.5$ kpc (\textit{bottom}). Within each panel, curves of different color represent the distributions of stars binned by Galactocentric radius $R_{\rm gal}$, from $3\leq R_{\rm gal}<5$ kpc (yellow) to $13\leq R_{\rm gal}<15$ kpc (blue). Each distribution is normalized so the area under the curve is 1, and the vertical scale is consistent across each row. All distributions are convolved with observational uncertainties in APOGEE DR17 (see Table \ref{tab:uncertainties}) and smoothed with a box-car width of 0.2 dex. In all cases an exponential DTD with timescale $\tau=1.5$ Gyr is assumed. Distributions from APOGEE DR17, binned similarly, are presented in the right-most column for reference.}
    \label{fig:feh-df-sfh}
    \script{feh_df_sfh.py}
\end{figure*}

Holding the SFH fixed, varying the DTD has only a minor effect on the MDF. Figure \ref{fig:feh-df-dtd} plots the [Fe/H] distributions for two multi-zone simulations which both assume an inside-out SFH but different DTDs: a power-law with slope $\alpha=-1.4$, and an exponential with timescale $\tau=3$ Gyr. The balance between prompt and delayed SNe Ia is starkly different between the two models, with $\sim 80\%$ of SNe Ia exploding within 1 Gyr in the former model but only $\sim 30\%$ in the latter. Nevertheless, the effect of the DTD on the MDF is second-order compared to the effect of the SFH as seen in Figure \ref{fig:feh-df-sfh}.

@@

\begin{figure}
    \centering
    \includegraphics{figures/ofe_feh_sfh.pdf}
    \caption{A comparison of the [O/Fe]--[Fe/H] plane between the four SFH models in our multi-zone simulations. All assume an exponential DTD with $\tau=1.5$ Gyr. Each point plots the abundances of a single star particle and is color-coded according to its Galactocentric radius at birth. Each panel plots a random sample of 10,000 star particles in the Solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) weighted by their mass. A Gaussian scatter has been applied to all points based on the median abundance errors in APOGEE DR17. The black curves represent the ISM abundance tracks in the 8 kpc zone. The red contours represent the APOGEE abundance distribution, with the solid and dashed contours enclosing 68\% and 95\% of stars, respectively.}
    \label{fig:ofe-feh-sfh}
    \script{ofe-feh-sfh.py}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{figures/age_ofe_sfh.pdf}
    \caption{Caption}
    \label{fig:age-ofe-sfh}
    \script{age_ofe_sfh.py}
\end{figure}

@@

    \item Our diagnostics consistently favor a DTD with a large fraction of delayed SNe Ia, such as the 3 Gyr exponential, 1 Gyr plateau, or triple system evolution models, over a DTD with a high number of prompt SNe Ia, such as the $t^{-1.4}$ power law or prompt models. [Discuss the disconnect and/or complement with \citet{Maoz2017-CosmicDTD}, etc.; something about different timescales probed by volumetric surveys vs. us]

@@

>>>>

We explore five different functional forms for the SN Ia DTD: a power-law, a broken power-law with an initial flat plateau, an exponential, a two-population model, and a model based on triple-system dynamics, with a one or two different parameterizations for each. Figure \ref{fig:dtds} presents these DTDs as a function of time since star formation.

@@

\paragraph{Two-population} A DTD in which 50\% of SNe Ia belong to a ``prompt'' Gaussian component at small $t$ and the other 50\% form an exponential tail at large $t$, normalized by $D_{t_p,\sigma,\tau}$:
\begin{equation}
    R(t) = D_{t_p,\sigma,\tau} \Big[e^{-\frac{(t-t_p)^2}{2\sigma^2}} + e^{-t/\tau}\Big]
    \label{eq:prompt-dtd}
\end{equation}
Following the two-population model from \citet{Mannucci2006-TwoPopulations}, we take $t_p=50$ Myr, $\sigma=15$ Myr, and $\tau=3$ Gyr, which results in roughly 50\% of SNe Ia exploding within $t<100$ Myr.

@@

\begin{deluxetable*}{lll}
\tablecaption{Summary of SN Ia DTD models explored in this paper.\label{tab:dtds}}
\tablehead{
\colhead{Model} & \colhead{Parameters} & \colhead{Similar to}
}
\startdata
Power-law   & $\alpha=-1.1$                 & \citet[][field]{Maoz2017-CosmicDTD}; 
                                              \citet{Wiseman2021-DESRates}              \\
Power-law   & $\alpha=-1.4$                 & \citet[][cluster]{Maoz2017-CosmicDTD}; 
                                              \citet{Heringer2019-FieldGalaxyDTD}       \\
Plateau     & $W=0.3$ Gyr, $\alpha=-1.1$    & \citet[][CLOSE DD]{Greggio2005-AnalyticalRates} \\
Plateau     & $W=1.0$ Gyr, $\alpha=-1.1$    & \citet[][WIDE DD]{Greggio2005-AnalyticalRates} \\
Triple-system   & $f_{\rm init}=0.05f_{\rm peak}$, $t_{\rm rise}=0.5$ Gyr, & \citet{Rajamuthukumar2022-TripleEvolution} \\
            & $W=0.5$ Gyr, $\alpha=-1.1$ & \\
Exponential & $\tau=1.5$ Gyr    & \citet[][SD]{Greggio2005-AnalyticalRates};
                                  \citet{Schonrich2009-RadialMixing};       \\
            &                   & \citet{Weinberg2017-ChemicalEquilibrium}  \\
Exponential & $\tau=3.0$ Gyr    & --- \\
Two-population  & $t_{\rm max}=0.05$ Gyr, $\sigma=0.015$ Gyr, & \citet{Mannucci2006-TwoPopulations} \\
            & $\tau=3.0$ Gyr & \\
\enddata
\end{deluxetable*}

@@

\begin{figure*}
    \centering
    \includegraphics{figures/star_formation_histories.pdf}
    \caption{The surface densities of star formation $\dot \Sigma_*$ (first row), gas infall $\dot \Sigma_{\rm in}$ (second row), and gas mass $\Sigma_{\rm gas}$ (third row), and the star formation efficiency timescale $\tau_*$ (fourth row) as functions of simulation time for our four model SFHs: inside-out (first column; see Equation \ref{eq:insideout-sfh}), late-burst (second column; see Equation \ref{eq:lateburst-sfh}), early-burst (third column; see Equations \ref{eq:earlyburst-ifr} and \ref{eq:earlyburst-taustar}), and two-infall (fourth column; see Equation \ref{eq:twoinfall-ifr}). In each panel, we plot curves for the zones which have inner radii at 4 kpc (yellow), 6 kpc (orange), 8 kpc (red), 10 kpc (violet), 12 kpc (indigo), and 14 kpc (blue).}
    \label{fig:sfhs}
    \script{star_formation_histories.py}
\end{figure*}

@@

All models are run for a duration of $t_{\rm max}=13.2$ Gyr with a time-step of $\Delta t=0.01$ Gyr. We adopt an outflow mass-loading factor $\eta\equiv \dot M_{\rm out}/\dot M_*=2.15$ \citep[see Equation 8 from][]{Johnson2021-Migration}, a star formation efficiency timescale $\tau_*\equiv M_{\rm gas}/\dot M_*=2$ Gyr, and an initial gas mass $M_{\rm gas,0}=0$. We adopt a continuous recycling prescription \citep[see Equation 2 from][]{JohnsonWeinberg2020-Starbursts}. Unless otherwise specified, we adopt the inside-out star formation rate (Equation \ref{eq:insideout-sfh}) evaluated at $R_{\rm gal}=8$ kpc (i.e., $\tau_{\rm rise}=2$ Gyr and $\tau_{\rm sfh}=15.1$ Gyr), and a minimum SN Ia delay time of 40 Myr. A summary of these one-zone fiducial parameters is presented in Table \ref{tab:onezone-parameters}.

@@

\subsection{The SN Ia Delay-Time Distribution}
\label{sec:onezone-dtd}

% Adjusting the parameters of the DTD affects how steeply the abundance track in [Fe/H]-[O/Fe] space falls from its initial ``plateau'' and the location of the ``knee.'' Figure \ref{fig:onezone-slope-timescale} shows abundance tracks from one-zone models which assume different slopes of a power-law DTD or different timescales of an exponential DTD. A steeper power-law slope results in a steeper decline in [O/Fe] and a lower knee, as does a shorter exponential timescale. The consequence is that a very shallow power-law produces a similar abundance track to a very steep exponential, which suggests these models may be difficult to distinguish in this parameter space. However, these cases can be distinguished by their MDFs and [O/Fe] distributions, where the power-law DTD produces a narrower, less skewed distribution while the exponential DTD produces a broader, more skewed distribution. In the [O/Fe] distribution especially, an exponential DTD with a 6 Gyr timescale produces a large number of high-$\alpha$ stars.

Figure \ref{fig:onezone-powerlaw-slope} compares the results of three one-zone models which are identical except for the slope of the power-law DTD. A steeper slope produces a sharper ``knee'' and a faster decline in [O/Fe], resulting in a narrower distribution of [O/Fe] around the low-$\alpha$ sequence and a dearth of high-$\alpha$ stars. Conversely, a shallower slope produces a gentler knee and slower decline in [O/Fe], resulting in a broader [O/Fe] distribution and a greater number of high-$\alpha$ stars. In all cases the [O/Fe] distribution is distinctly unimodal. The distribution of [Fe/H] is not as strongly affected by the power-law slope: a shallower slope results in only a modest increase in the width of the distribution.

\begin{figure}
    \centering
    \includegraphics{figures/onezone_powerlaw_slope.pdf}
    \caption{\textit{Center:} Abundance tracks in the [Fe/H]--[O/Fe] plane for one-zone models with a power-law DTD. The dotted, dashed, and solid curves represent models with power-law slopes $\alpha=-0.8$, $-1.1$, and $-1.4$, respectively. The open symbols located along each curve mark logarithmic steps in simulation time. In all cases a minimum SN Ia delay time of 40 Myr is assumed. \textit{Top:} Metalliticy distribution functions (MDFs) generated by the one-zone models. \textit{Right:} Distributions of [O/Fe] generated by the one-zone models.}
    \label{fig:onezone-powerlaw-slope}
    \script{onezone_powerlaw_slope.py}
\end{figure}

Similar trends can be seen when adjusting the timescale of the exponential DTD, as shown in Figure \ref{fig:onezone-exponential-timescale}. Here, the knee is not a sharp feature associated with the onset of SNe Ia as in the power-law case, but rather a gentle curve in the abundance track around 1 Gyr. A short exponential timescale shifts this knee down to lower [O/Fe] values, while a longer timescale raises it. The effect on the [O/Fe] distribution is similar to the power-law slope: a short timescale produces more low-$\alpha$ stars, while a long timescale produces more high-$\alpha$ stars (but still a unimodal distribution). The effect on the [Fe/H] distribution is somewhat more pronounced, with longer timescales skewing to lower [Fe/H] values. A doubling of the timescale from 1.5 Gyr to 3 Gyr raises the [O/Fe] abundance ratio at $t=1$ Gyr by $\sim0.05$ dex and at $t=3$ Gyr by $\sim0.1$ dex, but the equilibrium abundance reached at $t=10$ Gyr remains unchanged.

@@

\begin{figure}
    \centering
    \includegraphics{figures/onezone_twopopulation.pdf}
    \caption{One-zone model abundance tracks and distributions for variants of the two-population DTD.}
    \label{fig:onezone-prompt}
    \script{onezone_twopopulation.py}
\end{figure}

@@

A 150 Myr minimum delay time is incompatible with the two-population DTD model, which has $\sim 50$\% of SNe Ia explode in the first 100 Myr, and would have a negligible effect on the triple-system DTD as its relative SN Ia rate is so low at early times.

@@

% \begin{figure}
%     \centering
%     \includegraphics{figures/onezone_sfh.pdf}
%     \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with varying star formation history (SFH). An exponential DTD with $\tau=1.5$ Gyr is assumed in all models.}
%     \label{fig:onezone-sfh}
%     \script{onezone_sfh.py}
% \end{figure}

@@

@@

@@

\begin{figure*}
    \centering
    \includegraphics{figures/feh_df_sfh.pdf}
    \caption{Distributions of [Fe/H] for multi-zone simulations with different SFHs. Each row presents distributions of stars within a range of absolute midplane distance: $1\leq|z|<2$ kpc (\textit{top}), $0.5\leq|z|<1$ kpc (\textit{middle}), and $0\leq|z|<0.5$ kpc (\textit{bottom}). Within each panel, curves of different color represent the distributions of stars binned by Galactocentric radius $R_{\rm gal}$, from $3\leq R_{\rm gal}<5$ kpc (yellow) to $13\leq R_{\rm gal}<15$ kpc (blue). Each distribution is normalized so the area under the curve is 1, and the vertical scale is consistent across each row. All distributions are convolved with observational uncertainties in APOGEE DR17 (see Table \ref{tab:uncertainties}) and smoothed with a box-car width of 0.2 dex. In all cases an exponential DTD with timescale $\tau=1.5$ Gyr is assumed. Distributions from APOGEE DR17, binned and smoothed similarly, are presented in the right-most column for reference.}
    \label{fig:feh-df-sfh}
    \script{feh_df_sfh.py}
\end{figure*}

Holding the SFH fixed, varying the DTD has only a minor effect on the MDF across the disk. Figure \ref{fig:feh-df-dtd} plots the [Fe/H] distributions for two multi-zone simulations which both assume an inside-out SFH but different DTDs: a power-law with slope $\alpha=-1.4$, and an exponential with timescale $\tau=3$ Gyr. The balance between prompt and delayed SNe Ia is starkly different between the two models, with $\sim 80\%$ of SNe Ia exploding within 1 Gyr in the former model but only $\sim 30\%$ in the latter. Nevertheless, the effect of the DTD on the MDF is second-order compared to the effect of the SFH as seen in Figure \ref{fig:feh-df-sfh}.

@@

\begin{figure}
    \centering
    \includegraphics{figures/ofe_feh_sfh.pdf}
    \caption{A comparison of the [O/Fe]--[Fe/H] plane between the four SFH models in our multi-zone simulations. All assume an exponential DTD with $\tau=1.5$ Gyr. Each panel plots a random mass-weighted sample of 10,000 star particles in the Solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc) color-coded by the Galactocentric radius at birth. A Gaussian scatter has been applied to all points based on the median abundance errors in APOGEE DR17. The black curves represent the ISM abundance tracks in the 8 kpc zone. The red contours represent the APOGEE abundance distribution, with the solid and dashed contours enclosing 68\% and 95\% of stars, respectively.}
    \label{fig:ofe-feh-sfh}
    \script{ofe-feh-sfh.py}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics{figures/age_ofe_dtd.pdf}
    \caption{A comparison of the age--[O/Fe] relation between multi-zone simulations with different DTD models. All assume an inside-out SFH. Each row contains star particles from a different bin in $|z|$, with stars closest to the midplane in the bottom row and stars farthest from the midplane in the top row. Each panel plots a random mass-weighted sample of 10,000 star particles in the Solar annulus ($7\leq R_{\rm gal}<9$ kpc) color-coded by the Galactocentric radius at birth. A Gaussian scatter has been applied to all points based on the median [O/Fe] error from APOGEE DR17 and the median age error from \citet{Leung2023-Ages}. Black squares represent the mass-weighted median age of star particles within bins of [O/Fe] with a width of 0.05 dex, and the horizontal black error bars encompass the 16th and 84th percentiles. Red triangles represent the median age from \citet{Leung2023-Ages} in bins of [O/Fe], and the horizontal red error bars encompass the 16th and 84th percentiles. For clarity, bins which contain less than 1\% of the total mass (in the simulations) or total number of stars (in the data) are not plotted.}
    \label{fig:age-ofe-dtd}
    \script{age_ofe_dtd.py}
\end{figure*}

\begin{figure}
    \centering
    \includegraphics{figures/age_ofe_sfh.pdf}
    \caption{Similar to Figure \ref{fig:age-ofe-dtd} but for simulations with different SFH models. All assume an exponential DTD with $\tau=1.5$ Gyr. In all panels, stars are limited to the Solar neighborhood ($7\leq R_{\rm gal}<9$ kpc, $0\leq|z|<0.5$ kpc)}
    \label{fig:age-ofe-sfh}
    \script{age_ofe_sfh.py}
\end{figure}

@@

    \item Our diagnostics consistently favor a DTD with a large fraction of delayed SNe Ia, such as the 3 Gyr exponential, 1 Gyr plateau, or triple system evolution models, over a DTD with a high number of prompt SNe Ia, such as the $t^{-1.4}$ power-law or two-population models. [Discuss the disconnect and/or complement with \citet{Maoz2017-CosmicDTD}, etc.; something about different timescales probed by volumetric surveys vs. us]

@@

\section{Analytical DTDs}
\label{app:analytical-dtds}

Discuss \citet{Greggio2005-AnalyticalRates} vs our simple function approximations here?
